\vspace{-0.25em}\thetitle

### 2009-07-29 paper.tex
wip

We evaluate the quality of our packet size and inter-packet interval distribution predictions by looking at the distribution of K-S p-values for the predicted distribution versus the observed sample.
In theory, if the predictions are all correct, the p-values should be uniformly distributed on the interval [0,1].
In practice, however, the K-S test is not perfect, and its p-values are not uniform.
Instead of comparing predictions to the theoretical ideal of uniformity, we use a more pragmatic ideal as a baseline:
p-values of samples that are actually drawn from the predicted distributions.
We measure quality of predictions by how much worse that this ideal the predictions are.

>>>>

\newfootnote{\ksidealnote}{If the K-S test were ideal, this pragmatic baseline would in fact be uniform. The fact that it is not demonstrates the imperfection of the K-S test.}

We evaluate the quality of our packet size and inter-packet interval distribution predictions by looking at the distribution of K-S p-values for the predicted distribution versus the observed sample.
In theory, if the predictions are all correct, the p-values should be uniformly distributed on the interval [0,1].
In practice, however, the K-S test is not perfect, and its p-values are not uniform.
Instead of comparing predictions to the theoretical ideal of uniformity, we use a more pragmatic ideal as a baseline:
p-values of samples that are actually drawn from the predicted distributions.
We measure quality of predictions by how much worse that this ideal the predictions are.\ksidealnote

\Figure{cdf} shows the the \caps{CDF}s p-values for our ideal baseline and the predicted packet size and inter-packet interval distributions.
For comparison, we also show the p-values results for two simplistic prediction techniques.
The first alternative prediction technique is to always predicting the mean behavior of the entire training trace.
This does not perform as badly as one might think it would---always guessing the average is not an abysmal failure.
The second alternative technique is to just guess what you've already seen.
We call this ``self-prediction.''
This is likely the best guess one can make about a flow, without having learned from any other flows:
just guess that it will keep doing what it has already done.
